Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_3_model.tex
Fix notations

Instead of using the standard self-attention module as in current
state-of-the-art GPT-2 decoder~\cite{Radford2019LanguageMA}, we find that
dynamic convolutions~\cite{Wu2018PayLA} are more efficient to train. Suppose
when decoding the $t$th token, we have at the $\ell$th block the input
$\bz_{\ell t} \in \mathbb{R}^{1024}$. If $\ell = 0$, then $\bz_{0t}$ is the
embedding of the previous token. Otherwise it is the output from the previous
transformer block. Given kernel size $K$ and 16 attention heads, for each head
$h \in \{1, 2, ..., 16\}$, we first project the current and last $K-1$ steps
using a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bz_{\ell,h,t-j}' &=& \text{GLU}(\bW_{z\ell h} \, \bz_{\ell,t-j} + \bb_{z\ell h})
\end{IEEEeqnarray*}
where $j \in \{0,1,...,K-1\}$, GLU is the gated linear unit activation
function~\cite{Dauphin2017GLU}, and $\bz_{\ell,h,t-j}' \in \mathbb{R}^{64}$.
The output of each head's dynamic convolution is the weighted sum of these
projected values:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell h t} &=& \sum_{j=0}^{K-1} \gamma_{\ell hj} \, \bz_{\ell, h, t-j}'
\end{IEEEeqnarray*}
where the weight $\gamma_{\ell hj}$ is a linear projection of the input,
followed by a softmax over the kernel window:
\begin{IEEEeqnarray*}{lCl}
   \gamma_{\ell hj} &=& \text{Softmax} \left( \bw^T_{\gamma \ell h} \,
      \bz_{\ell,h,t-j} \right)
\end{IEEEeqnarray*}
The overall output is the concatenation of all the head outputs, followed by
a feedforward with a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell t} &=& [ \tz_{\ell 1 t}, \tz_{\ell 2 t},..., \tz_{\ell 16 t} ] \\
   \bd_{\ell t} &=& \text{LayerNorm}\left( \bz_{\ell t} +
             \bW_{\tz \ell} \, \tz_{\ell t} + \bb_{\tz \ell} \right)
\end{IEEEeqnarray*}
Note that given kernel size $K$, we can attend to the current time step and the
last $K-1$ steps. Following closely to~\cite{Wu2018PayLA}, our decoder has 4
transformer blocks with kernel sizes 3, 7, 15, and 31, respectively. Thus the
final block output will have collected information from the last 51 tokens.

@@

Given $\bd_{\ell t} \in \mathbb{R}^{1024}$, the output of the dynamic
convolution at layer $\ell$, we can now attend over the image context using
multi-head attention, also with 16 heads. For each head $h \in \{1, 2, ...,
16\}$, we first do a linear projection of $\bd_{\ell t}$ and the image
embeddings $\bX_I$ into a query $\bq_{I \ell h t} \in \mathbb{R}^{64}$, a set
of keys $\bK_{I \ell h t} = \{\bk_{I \ell h t i} \in \mathbb{R}^{64}
\}_{i=1}^{49}$, and the corresponding values $\bV_{I \ell h t} = \{ \bv_{I \ell
h t i} \in \mathbb{R}^{64} \}_{i=1}^{49}$:
\begin{IEEEeqnarray*}{lCl}
   \bq_{I\ell ht} &=& \bW_{I \ell h q} \, \bd_{\ell t} \\
   \bk_{I\ell h i} &=& \bW_{I \ell h k} \, \bx_{I i}
      \qquad \forall i \in \{1, 2, ..., 49\}\\
   \bv_{I \ell h i} &=& \bW_{I \ell h v} \, \bx_{I i}
      \qquad \forall i \in \{1, 2, ..., 49\}
\end{IEEEeqnarray*}
Then the attended image for each head is the weighted sum of the values, where
the weights are obtained from the dot product between the query and key:
\begin{IEEEeqnarray*}{lCl}
   \lambda_{I \ell h i} &=&\text{softmax}\left(\bk_{I\ell h i}^T \bq_{I \ell ht} \right)\\
   \bx'_{I \ell h t} &=& \sum_{i = 1}^{49}
      \lambda_{I \ell h i} \, \bv_{I \ell h i}
\end{IEEEeqnarray*}
The attention from each head is then concatenated into $\bx'_{I\ell t} \in
\mathbb{R}^{1024}$:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{I\ell t} &=& [\tx_{I\ell 1 t}, \tx_{I\ell 2 t}, ..., \tx_{I\ell 16 t}]
\end{IEEEeqnarray*}
and the overall image attention $\tx_{I\ell t} \in \mathbb{R}^{1024}$ is obtained
after adding a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tx_{I \ell t} &=& \text{LayerNorm}(\bd_{\ell t} + \bx'_{I\ell t})
\end{IEEEeqnarray*}
We use the same multi-head attention mechanism (with different weight matrices)
to obtain the attended article $\tx_{T \ell}$ and the attended face $\tx_{F
\ell}$. These three are finally concatenated and fed through a feedforward
layer:
\begin{IEEEeqnarray*}{lCl}
   \tx_{C \ell t} &=& [\tx_{I \ell}, \tx_{T \ell t}, \tx_{F \ell}] \\
   \tx_{R \ell t} &=& \bW_{C \ell} \, \tx_{C \ell t} + \bb_{C \ell} \\
   \tx_{D \ell t} &=& \text{ReLU}(\bW_{R \ell} \, \tx_{R \ell t} + \bb_{R \ell} )\\
   \bz_{\ell + 1,t} &=& \text{LayerNorm}(\tx_{R \ell t} + \bW_{D \ell} \,
      \tx_{D \ell t} + \bb_{D \ell})
\end{IEEEeqnarray*}
The final output $\bz_{\ell + 1,t} \in \mathbb{R}^{1024}$ is used as the input
to the next transformer block, or if we are in the last block, it is used
to compute the logits over the token vocabulary.

>>>>

Instead of using the standard self-attention module as in current
state-of-the-art GPT-2 decoder~\cite{Radford2019LanguageMA}, we find that
dynamic convolutions~\cite{Wu2018PayLA} are more efficient to train. Suppose
when decoding the $t$th token, we have at the $\ell$th block the input
$\bz_{\ell t} \in \mathbb{R}^{1024}$. If $\ell = 0$, then $\bz_{0t}$ is the
embedding of the previous token. Otherwise it is the output from the previous
transformer block. Given kernel size $K$ and 16 attention heads, for each head
$h \in \{1, 2, ..., 16\}$, we first project the current and last $K-1$ steps
using a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bz_{\ell,h,t-j}' &=& \text{GLU}(\bW_{z\ell h} \, \bz_{\ell,t-j} + \bb_{z\ell h})
\end{IEEEeqnarray*}
where $j \in \{0,1,...,K-1\}$, GLU is the gated linear unit activation
function~\cite{Dauphin2017GLU}, and $\bz_{\ell,h,t-j}' \in \mathbb{R}^{64}$.
The output of each head's dynamic convolution is the weighted sum of these
projected values:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell h t} &=& \sum_{j=0}^{K-1} \gamma_{\ell hj} \, \bz_{\ell, h, t-j}'
\end{IEEEeqnarray*}
where the weight $\gamma_{\ell hj}$ is a linear projection of the input,
followed by a softmax over the kernel window:
\begin{IEEEeqnarray*}{lCl}
   \gamma_{\ell hj} &=& \text{Softmax} \left( \bw^T_{\gamma \ell h} \,
      \bz'_{\ell,h,t-j} \right)
\end{IEEEeqnarray*}
The overall output is the concatenation of all the head outputs, followed by
a feedforward with a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell t} &=& [ \tz_{\ell 1 t}, \tz_{\ell 2 t},..., \tz_{\ell 16 t} ] \\
   \bd_{\ell t} &=& \text{LayerNorm}\left( \bz_{\ell t} +
             \bW_{\tz \ell} \, \tz_{\ell t} + \bb_{\tz \ell} \right)
\end{IEEEeqnarray*}
Note that given kernel size $K$, we can attend to the current time step and the
last $K-1$ steps. Following closely to~\cite{Wu2018PayLA}, our decoder has 4
transformer blocks with kernel sizes 3, 7, 15, and 31, respectively. Thus the
final block output will have collected information from the last 51 tokens.

@@

Given $\bd_{\ell t} \in \mathbb{R}^{1024}$, the output of the dynamic
convolution at layer $\ell$, we can now attend over the image context using
multi-head attention, also with 16 heads. For each head $h \in \{1, 2, ...,
16\}$, we first do a linear projection of $\bd_{\ell t}$ and the image
embeddings $\bX_I$ into a query $\bq_{I \ell h t} \in \mathbb{R}^{64}$, a set
of keys $\bK_{I \ell h t} = \{\bk_{I \ell h t i} \in \mathbb{R}^{64}
\}_{i=1}^{49}$, and the corresponding values $\bV_{I \ell h t} = \{ \bv_{I \ell
h t i} \in \mathbb{R}^{64} \}_{i=1}^{49}$:
\begin{IEEEeqnarray*}{lCl}
   \bq_{I\ell ht} &=& \bW_{I \ell h q} \, \bd_{\ell t} \\
   \bk_{I\ell h i} &=& \bW_{I \ell h k} \, \bx_{I i}
      \qquad \forall i \in \{1, 2, ..., 49\}\\
   \bv_{I \ell h i} &=& \bW_{I \ell h v} \, \bx_{I i}
      \qquad \forall i \in \{1, 2, ..., 49\}
\end{IEEEeqnarray*}
Then the attended image for each head is the weighted sum of the values, where
the weights are obtained from the dot product between the query and key:
\begin{IEEEeqnarray*}{lCl}
   \lambda_{I \ell h i} &=&\text{softmax}\left(\bk_{I\ell h i}^T \bq_{I \ell ht} \right)\\
   \bx'_{I \ell h t} &=& \sum_{i = 1}^{49}
      \lambda_{I \ell h i} \, \bv_{I \ell h i}
\end{IEEEeqnarray*}
The attention from each head is then concatenated into $\bx'_{I\ell t} \in
\mathbb{R}^{1024}$:
\begin{IEEEeqnarray*}{lCl}
   \bx'_{I\ell t} &=& [\tx_{I\ell 1 t}, \tx_{I\ell 2 t}, ..., \tx_{I\ell 16 t}]
\end{IEEEeqnarray*}
and the overall image attention $\tx_{I\ell t} \in \mathbb{R}^{1024}$ is obtained
after adding a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tx_{I \ell t} &=& \text{LayerNorm}(\bd_{\ell t} + \bx'_{I\ell t})
\end{IEEEeqnarray*}
We use the same multi-head attention mechanism (with different weight matrices)
to obtain the attended article $\tx_{T \ell t}$ and the attended face $\tx_{F
\ell t}$. These three are finally concatenated and fed through a feedforward
layer:
\begin{IEEEeqnarray*}{lCl}
   \tx_{C \ell t} &=& [\tx_{I \ell t}, \tx_{T \ell t}, \tx_{F \ell t}] \\
   \tx_{R \ell t} &=& \bW_{C \ell} \, \tx_{C \ell t} + \bb_{C \ell} \\
   \tx_{D \ell t} &=& \text{ReLU}(\bW_{R \ell} \, \tx_{R \ell t} + \bb_{R \ell} )\\
   \bz_{\ell + 1,t} &=& \text{LayerNorm}(\tx_{R \ell t} + \bW_{D \ell} \,
      \tx_{D \ell t} + \bb_{D \ell})
\end{IEEEeqnarray*}
The final output $\bz_{\ell + 1,t} \in \mathbb{R}^{1024}$ is used as the input
to the next transformer block, or if we are in the last block, it is used
to compute the logits over the token vocabulary.
